Summer Peaks and Winter Lows: An Analysis of Toronto Island Ferry Ticket Counts

### 2024-09-25 Paper/Paper.qmd
worked on peer review feedback, changed some written content, modified the tests to test the cleaned data and added them to the data_cleaning R script, made some changes in the paper.qmd based on peer feedback

---
title: "Navigating Trends: Analyzing Ticket Sales and Redemption Patterns For Toronto Island Ferries"
author: Krishna Kumar
thanks: "Code and data are available at: https://github.com/krishnak30/Toronto-Island-Ferry-Ticket-Counts-Krishna-K.git."
date: today
date-format: long
abstract: "This report looks at the ferry services to the Toronto Islands, a significant recreational destination accessible exclusively by water. We analyze a data set of Ferry Ticket Counts from May 2018 to September 2024 in order to find patterns and trends in ferry usage and the effects of external factors. Using time series analysis and data visualization, the data shows that there exist definitive seasonal trends, with sharp declines during the pandemic period. Our findings suggest that ferry usage is highly seasonal and very vulnerable to external shocks. The paper concludes by discussing broader implications for tourism, urban and contingency planning, and public transportation management."
format: pdf
number-sections: true
bibliography: references.bib
execute:
  echo: false     # Hide code globally
  warning: false  # Suppress warnings globally
  message: false  # Suppress messages globally
references: true
fig-align: center 
---

@@

The data used in this paper is derived from Open Data Toronto and is read into this paper using the library opendatatoronto [@opendatatoronto]. The data were cleaned and analyzed using the statistical programming language R [@R]. Simulating, cleaning, and testing the data was done with the help of the following packages: tidyverse [@tidyverse], janitor [@janitor], knitr [@knitr], kableExtra [@kableExtra], dplyr [@dplyr], readr [@readr], here [@here], and lubridate [@lubridate]. The graphs and plots were made using ggplot2 [@ggplot2].

@@

Interestingly, every month shows the close correlation between the sales and redemption tickets and what implications this has for the ferry service.

>>>>

---
title: "Summer Peaks and Winter Lows: An Analysis of Toronto Island Ferry Ticket Counts"
subtitle: "What Six Years of Data Reveal About Ferry Usage, Visitor Patterns, and Seasonal Consumer Behaviour"
author: Krishna Kumar
thanks: "Code and data are available at: https://github.com/krishnak30/Toronto-Island-Ferry-Ticket-Counts-Krishna-K.git."
date: today
date-format: long
abstract: "This report looks at the ferry services to the Toronto Islands, a significant recreational destination accessible exclusively by water. We analyze a data set of Ferry Ticket Counts from May 2018 to September 2024 in order to find patterns and trends in ferry usage and the effects of external factors. Using time series analysis and data visualization, the data shows that there exist definitive seasonal trends, with sharp declines during the pandemic period. Our findings suggest that ferry usage is highly seasonal and very vulnerable to external shocks. The paper concludes by discussing broader implications for tourism, urban and contingency planning, and public transportation management."
format: pdf
number-sections: true
bibliography: references.bib
execute:
  echo: false     # Hide code globally
  warning: false  # Suppress warnings globally
  message: false  # Suppress messages globally
references: true
fig-align: center 
---

@@

The data used in this paper is derived from Open Data Toronto and is read into this paper using the library 'opendatatoronto' [@opendatatoronto]. The data were cleaned and analyzed using the statistical programming language 'R' [@R]. Simulating, cleaning, and testing the data was done with the help of the following packages: 'tidyverse' [@tidyverse], 'janitor' [@janitor], 'knitr' [@knitr], 'kableExtra' [@kableExtra], 'dplyr' [@dplyr], 'readr' [@readr], 'here' [@here], and 'lubridate' [@lubridate]. The graphs and plots were made using 'ggplot2' [@ggplot2].

@@

Interestingly, every month shows a close correlation between the sales and redemption tickets and what implications this has for the ferry service. The values for sales and redemption ticket counts are extremely close together for all months as displayed in @fig-monthanalysis.
